---
title: "cluster runs for u'(x,t=1) and u(x,t=1) checking"
author: "Isabel Kim"
date: "5/10/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters:

* a = 0.02
* sigma = 0.01
* uhat = 40%
* b = 1
* k = 0.2

## Expectations:

* When x < -a/2 (x = 0.47):
  + Expected u'(x=0.47,t=1) = 0.05850982
  + Expected u(x=0.47, t=1) = 0.05098523
* When -a/2 <= x <= a/2 (x = 0.50):
  + Expected u'(x=0.5, t=1) = 0.6321206
  + Expected u(x=0.5, t=1) = 0.6537119
* When x > a/2 (x = 0.54):
  + Expected u'(x=0.54, t=1) = 0.02152456
  + Expected u(x=0.54, t=1) = 0.01833609
  
## Current data (40-100 replicates):

* When x < -a/2 (x = 0.47):
  + u’(x,t=1) observed: 0.0545 (close)
  + u(x,t=1) observed: 0.0412 (too low)
* When -a/2 <= x <= a/2 (x = 0.5):
  + u’(x,t=1) observed: 0.638 (close)
  + u(x,t=1) observed: 0.6475 (close)
* When x > a/2 (x = 0.54):
  + u’(x,t=1) observed: 0.0202
  + u(x,t=1) observed: 0.0161
  
## Cluster script

Output will look like this:
```{R eval=F}
Bounds of drive in generation 10: 0.490045 to 0.509809
----------------------
u'(x,t=1):
GENERATION: 10
UPRIME_X1:: 0.137931
UPRIME_X2:: 0.6
UPRIME_X3:: 0.0
u(x,t=1):
----------------------

GENERATION: 11
U_X1:: 0.108108
U_X2:: 0.673077
U_X3:: 0.0
----------------------
```

Take this output and create 6 columns:

1. u'(0.47,1), u'(0.5, 1), u'(0.54, 1), u(0.47,1), u(0.5,1), u(0.54,1)

## Cluster files

* Python driver: `/home/ikk23/underdom/main_scripts/python_u_driver.py`
* SLiM script: `/home/ikk23/underdom/main_scripts/nonWF-model.slim`
* Text file: `/home/ikk23/underdom/text_files/may10_u_runs.txt`
  + 50 array job
  + Each has 20 replicates
* Main cluster script: `/home/ikk23/underdom/u_runs_script/may10_u_runs.sh`
  + Submitted at 9:12pm on May 10th
* Merge cluster script: `/home/ikk23/underdom/merge_scripts/may10_u_runs_merge.sh`
  + Creates `/home/ikk23/underdom/csvs/u_check_with_a0.02.csv`
  + Submitted at 9:19pm on May 10th
  + On my local computer: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/u_check_with_a0.02.csv`
  
## New averages
```{r}
library(tidyverse)
data = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/u_check_with_a0.02.csv")

uprime_x1 = mean(data$`u'(x=0.47)`)
uprime_x2 = mean(data$`u'(x=0.5)`)
uprime_x3 = mean(data$`u'(x=0.54)`)
u_x1 = mean(data$`u(x=0.47)`)
u_x2 = mean(data$`u(x=0.5)`)
u_x3 = mean(data$`u(x=0.54)`)

print(paste0("Expected u'(x=0.47, t=1) = ",0.05850982, " vs observed = ", uprime_x1, " -- percent difference = ", (abs(0.05850982-uprime_x1)/0.05850982)*100))

print(paste0("Expected u(x=0.47, t=1) = ",0.05098523, " vs observed = ", u_x1, " -- percent difference = ", (abs(0.05098523-u_x1)/0.05098523)*100))

print(paste0("Expected u'(x=0.5, t=1) = ",0.6321206, " vs observed = ", uprime_x2, " -- percent difference = ", (abs(0.6321206-uprime_x2)/0.6321206)*100))

print(paste0("Expected u(x=0.5, t=1) = ", 0.6537119, " vs observed = ", u_x2, " -- percent difference = ", (abs(0.6537119-u_x2)/0.6537119)*100))

print(paste0("Expected u'(x=0.54, t=1) = ",0.02152456, " vs observed = ", uprime_x3, " -- percent difference = ", (abs(0.02152456-uprime_x3)/0.02152456)*100))

print(paste0("Expected u(x=0.54, t=1) = ",0.01833609, " vs observed = ", u_x3, " -- percent difference = ", (abs(0.01833609-u_x3)/0.01833609)*100))

```

Good - results are extremely close to the mathematical formulas when the number of replicates is large.