---
title: "Drive homozygotes"
author: "Isabel Kim"
date: "5/12/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Files

* SLiM: `nonWF-model-drive-homozygotes.slim`
* Python driver: `python_driver_homozygotes.py`
* Text file: `may12_ndd.txt`
* Script: `may12_ndd.sh`
  + Uses `a = 0.02, 0.07, 0.1, 0.25`
  + 20 replicates each
  + 100 lines * 20 replicates = 2000 lines per `.part` csv file
  + Submitted on 5/12 11:45am
* Results are in `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_csvs/`
  + `a0.02.csv` has header
  + `a0.07.csv` has no header
  + `a0.1.csv` has no header
  + `a0.25.csv` has no header

## Go through each file, average over the generations, and plot the number of drive homozygotes over time

### a = 0.02

```{r}
library(tidyverse)
a0_02 = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_csvs/a0.02.csv")

generations_vector = min(a0_02$gen):max(a0_02$gen)
n = length(generations_vector)
avg_ndd = rep(-1, n)
a_vec = rep(0.02, n)
number_of_replicates = rep(-1,n)
for (i in 1:n){
  g = generations_vector[i]
  rows_of_gen = a0_02 %>% filter(gen==g)
  avg_ndd[i] = mean(rows_of_gen$num_dd)
  number_of_replicates[i] = nrow(rows_of_gen)
}

avg_a_0.02_data = tibble(a = a_vec, generation = generations_vector, avg_ndd = avg_ndd, number_of_replicates = number_of_replicates)

a_0.02_plot = ggplot(avg_a_0.02_data, aes(x = generation, y = avg_ndd)) + theme_minimal() + geom_line(color = "red") + xlab("generation") + ylab("average number of homozygotes") + ggtitle("a = 0.02 -- 20 replicates")

#ggsave(filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_figs/a_0.02_avg_ndd.png", plot = a_0.02_plot)

a_0.02_plot
```

### a = 0.07

```{r}
a0_07 = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_csvs/a0.07.csv", col_names = c("a","replicate","gen","num_dd" ))

generations_vector = min(a0_07$gen):max(a0_07$gen)
n = length(generations_vector)
avg_ndd = rep(-1, n)
a_vec = rep(0.07, n)
number_of_replicates = rep(-1,n)
for (i in 1:n){
  g = generations_vector[i]
  rows_of_gen = a0_07 %>% filter(gen==g)
  avg_ndd[i] = mean(rows_of_gen$num_dd)
  number_of_replicates[i] = nrow(rows_of_gen)
}

avg_a_0.07_data = tibble(a = a_vec, generation = generations_vector, avg_ndd = avg_ndd, number_of_replicates = number_of_replicates)

a_0.07_plot = ggplot(avg_a_0.07_data, aes(x = generation, y = avg_ndd)) + theme_minimal() + geom_line(color = "red") + xlab("generation") + ylab("average number of homozygotes") + ggtitle("a = 0.07 -- 20 replicates")

#ggsave(filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_figs/a_0.07_avg_ndd.png", plot = a_0.07_plot)

a_0.07_plot
```

### a = 0.1

```{r}
a0_1 = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_csvs/a0.1.csv", col_names = c("a","replicate","gen","num_dd" ))

generations_vector = min(a0_1$gen):max(a0_1$gen)
n = length(generations_vector)
avg_ndd = rep(-1, n)
a_vec = rep(0.1, n)
number_of_replicates = rep(-1,n)
for (i in 1:n){
  g = generations_vector[i]
  rows_of_gen = a0_1 %>% filter(gen==g)
  avg_ndd[i] = mean(rows_of_gen$num_dd)
  number_of_replicates[i] = nrow(rows_of_gen)
}

avg_a_0.1_data = tibble(a = a_vec, generation = generations_vector, avg_ndd = avg_ndd, number_of_replicates = number_of_replicates)

a_0.1_plot = ggplot(avg_a_0.1_data, aes(x = generation, y = avg_ndd)) + theme_minimal() + geom_line(color = "red") + xlab("generation") + ylab("average number of homozygotes") + ggtitle("a = 0.1 -- 20 replicates")

#ggsave(filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_figs/a_0.1_avg_ndd.png", plot = a_0.1_plot)

a_0.1_plot
```


### a = 0.25

```{r}
a0_25 = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_csvs/a0.25.csv", col_names = c("a","replicate","gen","num_dd" ))

generations_vector = min(a0_25$gen):max(a0_25$gen)
n = length(generations_vector)
avg_ndd = rep(-1, n)
a_vec = rep(0.25, n)
number_of_replicates = rep(-1,n)
for (i in 1:n){
  g = generations_vector[i]
  rows_of_gen = a0_25 %>% filter(gen==g)
  avg_ndd[i] = mean(rows_of_gen$num_dd)
  number_of_replicates[i] = nrow(rows_of_gen)
}

avg_a_0.25_data = tibble(a = a_vec, generation = generations_vector, avg_ndd = avg_ndd, number_of_replicates = number_of_replicates)

a_0.25_plot = ggplot(avg_a_0.25_data, aes(x = generation, y = avg_ndd)) + theme_minimal() + geom_line(color = "red") + xlab("generation") + ylab("average number of homozygotes") + ggtitle("a = 0.25 -- 20 replicates")

#ggsave(filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/cluster_figs/a_0.25_avg_ndd.png", plot = a_0.25_plot)

a_0.25_plot
```