---
title: "Examples of the R-simulated bistable waves"
author: "Isabel Kim"
date: "4/27/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load in the functions 
```{r}
source("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/scripts/bistable-wave.R")
```

* Use the `simulate_u_x_t(u, x_grid,time_steps, D, k,uhat, save_plot_path)` function
  + Note that the initial `u` must be twice differentiable

## Gaussian u(x)

### D = 0.01, k = 0.2, uhat = 0.4
```{r}
x_grid = seq(-10, 10, length.out = 1000)
u = dnorm(x_grid)*2.506754 # make u(x=0)=1

simulate_u_x_t(u, x_grid, 11, 0.01, 0.2, 0.4)
```

* The approximation breaks down at t=11.
* The wave goes a bit lower than 1 from t=1 to t=5 but then rises from t=6 to t=10
  + The whole time, the wave is widening
* Possible that the wave falls and widens, then rises back up to 1 and fixes
  + Could correspond to a dip in the frequency of the drive at x=0 in the first few generations and a gradual build up back to 1


### Raise D to 0.02; keep k=0.2 and uhat=0.4
```{r}
x_grid = seq(-10, 10, length.out = 1000)
u = dnorm(x_grid)*2.506754 # make u(x=0)=1
simulate_u_x_t(u, x_grid, 9, 0.02, 0.2, 0.4)
```

* Falls and widens
* Looks like it starts to rise again around t=8
* Approximation breaks down at t=9


### Lower D to 0.009; keep k=0.2 and uhat=0.4
```{r}
x_grid = seq(-10, 10, length.out = 1000)
u = dnorm(x_grid)*2.506754 # make u(x=0)=1
simulate_u_x_t(u, x_grid, 12, 0.009, 0.2, 0.4, "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/D0.009_k0.2_uhat0.4.gif")
```
* D is still sufficient; the wave falls a bit and widens but then rises back to 1 by t=11
* Approximation then breaks down at t=12

* Would be useful to have a measurement of how the critical AUC is changing over time

## Let's make D too small

### D = 0.003; keep k=0.2 and uhat=0.4
```{r}
x_grid = seq(-10, 10, length.out = 1000)
u = dnorm(x_grid)*2.506754 # make u(x=0)=1
simulate_u_x_t(u, x_grid, 12, 0.003, 0.2, 0.4)
```
* Doesn't fall, just widens at the top
* Is this helpful? Or are we just scaling down time?

### D = 0.001; keep k=0.2 and uhat=0.4
```{r}
x_grid = seq(-10, 10, length.out = 1000)
u = dnorm(x_grid)*2.506754 # make u(x=0)=1
simulate_u_x_t(u, x_grid, 12, 0.001, 0.2, 0.4)
```
 * Doesn't fall, just widens a bit
 
 
### D = 0.0009; keep k=0.2 and uhat=0.4
```{r}
x_grid = seq(-10, 10, length.out = 1000)
u = dnorm(x_grid)*2.506754 # make u(x=0)=1
simulate_u_x_t(u, x_grid, 12, 0.0003, 0.2, 0.4)
```
* Even when D is extremely small, the wave widens