---
title: "Wave width"
author: "Isabel Kim"
date: "5/11/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load in functions

```{r}
library(tidyverse)
source("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/scripts/u_functions.R")
```

## One parameter set

```{r}
a = 0.07
print(paste0("Drive is between ",0.5-(a/2)," and ",0.5+(a/2)))
sigma = 0.01
uhat = 0.4
b = 1
k=0.2 
alpha =  1 - (2*uhat)
d_d_fitness = 	1 + (2*alpha*k)
d_wt_fitness = 1 + ((alpha-1)*k)
wt_wt_fitness = 1
print(paste("d/d fitness:", d_d_fitness, "d/wt fitness:", d_wt_fitness, "wt/wt fitness:", wt_wt_fitness))
find_wave_width(a,b,sigma,k,uhat)
```

Predict x bounds to be 0.4626925 and 0.5373075. u(x,t=1) > uhat, so we predict the drive to succeed.

**Will need to run this code on each a value of the past data and see the P(increase) vs a plot --> prediction vs truth**

### SLiM widths (check to ensure they're close to the prediction, on average)

Note that the precision is restricted by the number of cells (200 -- each cell has a width of 0.005).

* Replicate 1: 0.4625 and 0.5375
* Replicate 2: 0.4625 and 0.5375
* Replicate 3: 0.4625 and 0.5375
* Replicate 4: 0.4625 and 0.5375
* Replicate 5: 0.4625 and 0.5375

```{r}
p_error_left = (abs(0.4626925-0.4625)/0.4626925)*100
p_error_right = (abs(0.5373075-0.5375)/0.5373075)*100

print(paste0(round(p_error_left,4), "% error for x_left and ", round(p_error_right,4), "% error for x_right"))
```

Conclusion: the wave width matches the mathematical prediction very well.

## Old uhat=40% data from the cluster -- load this in, find wave width for each value of a, and see if when d > a, the drive is more likely to succeed

* Summary csv: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/cluster/u_hat=0.4_run/csvs/summary_uhat40_april19_a_full_vs_outcome.csv`

```{r}
library(tidyverse)

# uhat = 40% data 
data = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/cluster/u_hat=0.4_run/csvs/summary_uhat40_april19_a_full_vs_outcome.csv")

# other parameters
find_wave_width(a,b,sigma,k,uhat)

b = 1
sigma = 0.01
k = 0.2
uhat = 0.4

n = nrow(data)
wave_width_vector = rep(-1,n)
increase_in_wave_width_vector = rep(-1, n)
for (i in 1:n){
  a = data$a[i]
  res = find_wave_width(a,b,sigma,k,uhat, plot = FALSE)
  wave_width_vector[i] = res$wave_width
  increase_in_wave_width_vector[i] = res$change_in_wave_width
}

edit_data = data %>% add_column(wave_width = wave_width_vector,
                                increase_in_wave_width = increase_in_wave_width_vector)
```

### Plots

#### a vs change in wave width

```{r}
a_vs_change_width = ggplot(edit_data, aes(a,increase_in_wave_width)) + geom_line(color="red") + xlab("a") + ylab("d - a") + geom_hline(yintercept = 0) + theme_minimal()

(a_vs_change_width)
```

#### Which value of a --> d = a? Which value gave no AUC change?

```{r}
# get rid of the a = 1 row
edit_data = edit_data %>% filter(a!=1)

indices_in_order = order(abs(edit_data$increase_in_wave_width))
lowest_width_change_index = indices_in_order[1]
row_no_change_in_width = edit_data[lowest_width_change_index,]
a_no_change_in_width = row_no_change_in_width$a


indices_in_order_delta = order(abs(edit_data$delta))
lowest_delta_index = indices_in_order_delta[1]
row_no_auc_change = edit_data[lowest_delta_index,]
a_no_change_in_auc = row_no_auc_change$a

closest_to_p_increase_of_50_indices_in_order = order(abs(edit_data$p_increase - 0.5))
closest_to_50_index = closest_to_p_increase_of_50_indices_in_order[1]
row_p_increase_50 = edit_data[closest_to_50_index,]
a_p_increase_50 = row_p_increase_50$a
```

#### Replot a vs P(increase) with lines for a that gives d = a and a that gives AUC1 = ab, vs the true a that caused P(increase) = 50%

```{r}
a_vs_p_increase = ggplot(edit_data, aes(x=a,y=p_increase)) + geom_point(color = "red") + theme_minimal() + xlab("a") + ylab("P(increase)") + geom_vline(xintercept = a_no_change_in_width, color = "blue") + geom_vline(xintercept = a_no_change_in_auc, color = "yellow") + geom_vline(xintercept = a_p_increase_50, color = "red") + ggtitle("blue = a --> no change in wave width (0.0163) \nyellow = a --> no change in AUC (0.0256) \nred = a --> the observed P(increase)=50% (0.0694)") + xlim(0, 0.15)

a_vs_p_increase

#ggsave(plot=a_vs_p_increase, filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/a_vs_p_increase.png")
```

The value of a that causes no change in wave width is even further off than the value of a that causes no change in AUC.

#### Change in wave width vs P(increase)

```{r}
change_width_vs_p_increase = ggplot(edit_data, aes(x = increase_in_wave_width, y = p_increase)) + geom_point(color = "red") + theme_minimal() + xlab("d - a") + ylab("P(increase)") + geom_vline(xintercept=0)

change_width_vs_p_increase
#ggsave(plot = change_width_vs_p_increase, filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/bistable-R-waves/change_in_wave_width_vs_p_increase.png")
```