---
title: "uhat=40% a vs change in number of drive alleles"
author: "Isabel Kim"
date: "4/13/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

* For a given value of a:
  + Run SLiM 100 times
  + Obtain just the change in the number of drive alleles from gen11 to gen10
  + In csv, print *a* vs *change*
* Make sure there are a good amount of *a* values below a_predicted and above a_predicted (based on the delta equation)
* Other parameters to keep constant from run to run:
  + sigma = m = 0.01
  + k = 0.2
  + u_hat = 0.4
  + N = 30,000
  + Stop the simulation at generation 11
    * Changing the SLiM simulation to reflect this (transfer new version)
* Need a new python driver parsing function
  + `python_driver_num_drives.py` -- use this instead. Only need to specify -a

## a values from before

* The predicted value of a that will cause delta=0 is a_predicted = 0.0258
* But the observed value of a that caused P(increase)=50% was a_observed = 0.0682
* The value of a beyond which/at which P(increase)=100% was a_upper = 0.07884 --> round to 0.08

### Values to focus on

* focus mostly on a = 0.01 to a = 0.1
```{r}
a_values = seq(0.01,0.1,length.out=200) # 200 jobs --> a increases by 0.00045 only

a_pred_diff = abs(a_values - 0.0258)
a_pred_ind = which.min(a_pred_diff) # 36
a_value_concentrate = a_values[a_pred_ind] # the 36th job is a* = 0.02582915

a_obs_diff = abs(a_values - 0.0682)
a_obs_ind = which.min(a_obs_diff) # 130
a_obs_concentrate = a_values[a_obs_ind] # the 130th job is a_observed = 0.06834171
```

## Files

* slim file: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/slim/nonWF-model.slim`
  + on the cluster: `/home/ikk23/underdom/main_scripts/nonWF-model.slim`
* python driver (new): `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/cluster/python_driver_num_drives.py`   
  + on the cluster: `/home/ikk23/underdom/main_scripts/python_driver_num_drives.py`
* text file: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/cluster/u_hat=0.4_run/slurm_text/uhat40_a_vs_dr_change_april13.txt`
  + on the cluster: `/home/ikk23/underdom/text_files/uhat40_a_vs_dr_change_april13.txt`
* main SLURM script: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/cluster/u_hat=0.4_run/slurm_main/uhat40_april13_a_vs_change_main.sh`
  + on the cluster: `/home/ikk23/underdom/vary_a_scripts/uhat40_april13_a_vs_change_main.sh`
  + **Submitted batch job 4301202 on 4/13 at 7:06pm**
* merge SLURM script: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/cluster/u_hat=0.4_run/slurm_merge/uhat40_april13_a_vs_change_merge.sh`
  + creates: `/home/ikk23/underdom/out_u40/uhat40_april13_a_vs_change.csv` on the cluster
  + on the cluster: `/home/ikk23/underdom/merge_scripts/uhat40_april13_a_vs_change_merge.sh`
