---
title: "Check equations"
author: "Isabel Kim"
date: "6/10/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Equations

```{r}
# m = d/d drop size
# x = position, centered at 0 (subtract x = x_slim - 0.5)
# D = 0.5(sigma^2)
# rho = wild-type density
# k = selection coefficient
# uhat = invasion frequency (alpha = 1-2uhat)
expected_NAA_after_dispersal = function(m,x,D){
  numerator = m*exp((-x^2)/(4*D))
  denominator = sqrt(4*pi*D)
  return(numerator/denominator)
}

expected_Naa_after_dispersal = function(wild_type_popsize, cell_width){
  return(cell_width*wild_type_popsize)
}

expected_NAA_after_reproduction = function(m,x,D,rho){
  factor1_numerator = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  factor2_numerator = (m^2)*exp((-x^2)/(2*D))
  num = factor1_numerator*factor2_numerator
  
  denominator_term1_inner = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  denominator_term1 = denominator_term1_inner^2
  denominator_term2 = sqrt(4*pi*D)
  denom = denominator_term1*denominator_term2
  
  sol = (num/denom)
  return(sol)
}

expected_NAa_after_reproduction = function(m,x,D,rho){
  denominator_term1_inner = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  denominator_term1 = denominator_term1_inner^2
  denominator_term2 = sqrt(4*pi*D)
  denom = denominator_term1*denominator_term2
  
  numerator_factor1 = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  numerator_factor2 = 2*m*rho*exp((-x^2)/(4*D))*sqrt(4*pi*D)
  numerator = numerator_factor1*numerator_factor2
  
  sol = numerator/denom
  return(sol)
}

expected_Naa_after_reproduction = function(m,x,D,rho){
  denominator_term1_inner = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  denominator_term1 = denominator_term1_inner^2
  denominator_term2 = sqrt(4*pi*D)
  denom = denominator_term1*denominator_term2
  
  term1_num = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  term2_num = 4*pi*D*(rho^2)
  num = term1_num*term2_num
  
  sol = num/denom
  return(sol)
}

expected_NAA_after_viability = function(m,x,D,rho,uhat,k){
  alpha = 1-(2*uhat)
  
  f1_numerator = (1+(2*alpha*k))
  f2 = (m^2)*exp((-x^2)/(2*D))
  f3 = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  numerator = f1_numerator*f2*f3
  
  f1_denom = sqrt(4*pi*D)*(1 + (2*alpha*k))*(m^2)*exp((-x^2)/(2*D))
  f2_denom = 8*pi*D*rho*m*exp((-x^2)/(4*D))*(1 + ((alpha-1)*k))
  f3_denom = 4*pi*D*(rho^2)*sqrt(4*pi*D)
  denom = f1_denom+f2_denom+f3_denom
  
  sol = numerator/denom
  return(sol)
}

expected_NAa_after_viability = function(m,x,D,rho,uhat,k){
  alpha = 1-(2*uhat)
  
  f1_num = 1 + ((alpha-1)*k)
  f2_num = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  f3_num = 2*m*rho*exp((-x^2)/(4*D))
  num = f1_num*f2_num*f3_num
  
  denom_t1 = (1+(2*alpha*k))*(m^2)*exp((-x^2)/(2*D))
  denom_t2 = (1 + ((alpha-1)*k))*2*m*rho*exp((-x^2)/(4*D))*sqrt(4*pi*D)
  denom_t3 = 4*pi*D*(rho^2)
  denom = denom_t1+denom_t2+denom_t3
  
  sol = num/denom
  return(sol)
}

expected_Naa_after_viability = function(m,x,D,rho,uhat,k){
  
  alpha = 1-(2*uhat)
  
  f1_denom = sqrt(4*pi*D)*(1 + (2*alpha*k))*(m^2)*exp((-x^2)/(2*D))
  f2_denom = 8*pi*D*rho*m*exp((-x^2)/(4*D))*(1 + ((alpha-1)*k))
  f3_denom = 4*pi*D*(rho^2)*sqrt(4*pi*D)
  denom = f1_denom+f2_denom+f3_denom
  
  num_f1 = 4*pi*D*(rho^2)
  num_f2 = (m*exp((-x^2)/(4*D))) + (rho*sqrt(4*pi*D))
  num = num_f1*num_f2
  sol = num/denom
  
  return(sol)
}

all_expectations = function(m,x,D,rho,uhat,k){
  # after dispersal only
  nAA_prime = expected_NAA_after_dispersal(m,x,D)
  nAa_prime = 0
  naa_prime = rho
  
  # after dispersal and reproduction
  nAA_prime_prime = expected_NAA_after_reproduction(m,x,D,rho)
  nAa_prime_prime = expected_NAa_after_reproduction(m,x,D,rho)
  naa_prime_prime = expected_Naa_after_reproduction(m,x,D,rho)
  
  # after dispersal, reproduction, and viability selection
  nAA_t1 = expected_NAA_after_viability(m,x,D,rho,uhat,k)
  nAa_t1 = expected_NAa_after_viability(m,x,D,rho,uhat,k)
  naa_t1 = expected_Naa_after_viability(m,x,D,rho,uhat,k)
  
  results = list(nAA_after_dispersal = nAA_prime,
                 nAa_after_dispersal = nAa_prime,
                 naa_after_dispersal = naa_prime,
                 nAA_after_reproduction = nAA_prime_prime,
                 nAa_after_reproduction = nAa_prime_prime,
                 naa_after_reproduction = naa_prime_prime,
                 nAA_after_viability = nAA_t1,
                 nAa_after_viability = nAa_t1,
                 naa_after_viability = naa_t1)
  return(results)
}
```





## Expected counts for certain parameters

* m = d/d drop size
* x = position, centered at 0 (subtract x = x_slim - 0.5)
* D = 0.5(sigma^2)
* rho = wild-type density
* k = selection coefficient
* uhat = invasion frequency (alpha = 1-2uhat)

```{r}
m = 1000
D = 0.5*(0.01^2)
k = 0.2
uhat = 0.2
rho = 30000/30 # cell width of 0.01
x = 0.283333 - 0.5

all_expectations(m,x,D,rho,uhat,k)
```

## SLiM equations:

`x` is not adjusted yet.

```{bash eval=F}
numAA_after_dispersal(float x)

numAa_after_dispersal(float x)

numaa_after_dispersal(float x)

numAA_after_reproduction(float x)

numAa_after_reproduction(float x)

numaa_after_reproduction(float x)

numAA_after_viability(float x)

numAa_after_viability(float x)

numaa_after_viability(float x)
```

## Output analysis in Python script

* Line examples:
  + Generation10, after Gaussian dispersal: 
```{bash eval=F}
GEN10_after_dispersal:: X1:: 0.0333333 X2:: 0.0666667 MIDPT:: 0.05 N_DD:: 0.0 EXP_N_DD:: 0.0 N_DWT:: 0.0 EXP_N_DWT:: 0.0 N_WTWT:: 25890.0 EXP_N_WTWT:: 1000.0
```
  + Generation 11, after reproduction but before viability:
```{bash eval=F}
GEN11_after_reproduction:: X1:: 0.9 X2:: 0.933333 MIDPT:: 0.916667 N_DD:: 0.0 EXP_N_DD:: 0.0 N_DWT:: 0.0 EXP_N_DWT:: 0.0 N_WTWT:: 60240.0 EXP_N_WTWT:: 1000.0
```
  + Generation 11, after both reproduction and viability:
```{bash eval=F}
GEN11_after_viability:: X1:: 0.966667 X2:: 1.0 MIDPT:: 0.983333 N_DD:: 0.0 EXP_N_DD:: 0.0 N_DWT:: 0.0 EXP_N_DWT:: 0.0 N_WTWT:: 20490.0 EXP_N_WTWT:: 1000.0
```
* csv: `x1, x2, x_midpoint,time_point,n_dd, n_dwt, n_wt, exp_n_dd, exp_n_dwt, exp_n_wt` (10 columns)
  + time_point is either "after_dispersal", "after_reproduction", or "after_viability"


## Function to plot a genotype count vs expected count at a given time
```{r}
plot_count_vs_exp = function(csv, genotype, time_point, show_plot = TRUE){
  # csv = output of single-run-analyze-counts.py, read into R as a tibble
  # genotype = either "dd", "dwt", or "wtwt"
  # time_point = either "after_dispersal", "after_reproduction", or "after_viability"
  
  t = time_point
  filtered_csv = csv %>% filter(time_point == t)
  
  if (genotype == "dd"){
    p = ggplot(filtered_csv, aes(x = x_midpoint)) + 
      geom_line(aes(y=n_dd), color = "black") + geom_line(aes(y=exp_n_dd),color="red") + theme_minimal() + 
      ylab("count") + ggtitle(paste0("expected (red) and observed (black) d/d count ", t))
  } else if (genotype == "dwt"){
    p = ggplot(filtered_csv, aes(x = x_midpoint)) + 
      geom_line(aes(y=n_dwt), color = "black") + geom_line(aes(y=exp_n_dwt),color="red") + theme_minimal() + 
      ylab("count") + ggtitle(paste0("expected (red) and observed (black) d/wt count ", t))
  } else {
    p = ggplot(filtered_csv, aes(x = x_midpoint)) + 
      geom_line(aes(y=n_wtwt), color = "black") + geom_line(aes(y=exp_n_wt),color="red") + theme_minimal() + 
      ylab("count") + ggtitle(paste0("expected (red) and observed (black) wt/wt count ", t))
  }
  if (show_plot){
    print(p)
  }
  return(p)
}
```


## m=1000 run 

* uhat = k = 0.2
* wt size = 30,000
* local radius and mating radius = 0.001
* sigma = 0.01
```{bash eval=F}
TEXT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/m1000_k_uhat0.2.txt
CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat0.2.csv
PYTHON_SCRIPT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/single-run-analyze-counts.py

python $PYTHON_SCRIPT $TEXT > $CSV
```


```{r}
library(tidyverse)
csv = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat0.2.csv")

# Plot the after dispersal counts
after_dispersal_ndd = plot_count_vs_exp(csv, "dd","after_dispersal",FALSE)
after_dispersal_ndwt = plot_count_vs_exp(csv, "dwt","after_dispersal",FALSE)
after_dispersal_wtdwt = plot_count_vs_exp(csv, "wtwt","after_dispersal",FALSE)

print(after_dispersal_ndd)
print(after_dispersal_ndwt)
print(after_dispersal_wtdwt)

# Plot the after reproduction counts
after_rep_dd = plot_count_vs_exp(csv, "dd","after_reproduction",FALSE)
after_rep_dwt = plot_count_vs_exp(csv, "dwt","after_reproduction",FALSE)
after_rep_wtwt = plot_count_vs_exp(csv, "wtwt","after_reproduction",FALSE)

print(after_rep_dd)
print(after_rep_dwt)
print(after_rep_wtwt)

# Plot the after reproduction + viability counts
after_viab_dd = plot_count_vs_exp(csv, "dd","after_viability",FALSE)
after_viab_dwt = plot_count_vs_exp(csv, "dwt","after_viability",FALSE)
after_viab_wtwt = plot_count_vs_exp(csv, "wtwt","after_viability",FALSE)

print(after_viab_dd)
print(after_viab_dwt)
print(after_viab_wtwt)
```

The expectations are now much lower than the observed counts, especially for d/wt and wt/wt.

## Should rho = N_wildtypes? Before, I multiplied to approximate the number of wild-types. But (N_wildtypes*cellwidth)/cellwidth = N_wildtypes

```{bash eval=F}
TEXT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/m1000_k_uhat_0.2_N_rho.txt
CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat_0.2_N_rho.csv
PYTHON_SCRIPT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/single-run-analyze-counts.py

python $PYTHON_SCRIPT $TEXT > $CSV
```


```{r}
csv = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat_0.2_N_rho.csv")

# Plot the after dispersal counts
after_dispersal_ndd = plot_count_vs_exp(csv, "dd","after_dispersal",FALSE)
after_dispersal_ndwt = plot_count_vs_exp(csv, "dwt","after_dispersal",FALSE)
after_dispersal_wtdwt = plot_count_vs_exp(csv, "wtwt","after_dispersal",FALSE)

print(after_dispersal_ndd)
print(after_dispersal_ndwt)
print(after_dispersal_wtdwt)

# Plot the after reproduction counts
after_rep_dd = plot_count_vs_exp(csv, "dd","after_reproduction",FALSE)
after_rep_dwt = plot_count_vs_exp(csv, "dwt","after_reproduction",FALSE)
after_rep_wtwt = plot_count_vs_exp(csv, "wtwt","after_reproduction",FALSE)

print(after_rep_dd)
print(after_rep_dwt)
print(after_rep_wtwt)

# Plot the after reproduction + viability counts
after_viab_dd = plot_count_vs_exp(csv, "dd","after_viability",FALSE)
after_viab_dwt = plot_count_vs_exp(csv, "dwt","after_viability",FALSE)
after_viab_wtwt = plot_count_vs_exp(csv, "wtwt","after_viability",FALSE)

print(after_viab_dd)
print(after_viab_dwt)
print(after_viab_wtwt)
```
Now rho is wayyy too off.

## Try rho = N_wildtypes/cell_width
```{bash eval=F}
TEXT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/m1000_k_uhat_0.2_N_rho.txt
CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat_0.2_rho_div_width.csv
PYTHON_SCRIPT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/single-run-analyze-counts.py

python $PYTHON_SCRIPT $TEXT > $CSV
```

```{r}
csv = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat_0.2_rho_div_width.csv")

# Plot the after dispersal counts
after_dispersal_ndd = plot_count_vs_exp(csv, "dd","after_dispersal",FALSE)
after_dispersal_ndwt = plot_count_vs_exp(csv, "dwt","after_dispersal",FALSE)
after_dispersal_wtdwt = plot_count_vs_exp(csv, "wtwt","after_dispersal",FALSE)

print(after_dispersal_ndd)
print(after_dispersal_ndwt)
print(after_dispersal_wtdwt)

# Plot the after reproduction counts
after_rep_dd = plot_count_vs_exp(csv, "dd","after_reproduction",FALSE)
after_rep_dwt = plot_count_vs_exp(csv, "dwt","after_reproduction",FALSE)
after_rep_wtwt = plot_count_vs_exp(csv, "wtwt","after_reproduction",FALSE)

print(after_rep_dd)
print(after_rep_dwt)
print(after_rep_wtwt)

# Plot the after reproduction + viability counts
after_viab_dd = plot_count_vs_exp(csv, "dd","after_viability",FALSE)
after_viab_dwt = plot_count_vs_exp(csv, "dwt","after_viability",FALSE)
after_viab_wtwt = plot_count_vs_exp(csv, "wtwt","after_viability",FALSE)

print(after_viab_dd)
print(after_viab_dwt)
print(after_viab_wtwt)
```

## Should the observed counts *not* be divided by the width, but should the width be VERY small such that x=0.5-0.50001 is approximately x=0.5 (dividing by 0.0001 would really inflate this)?

Width of 0.01

```{bash eval=F}
TEXT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/m1000_k_uhat_0.2_N_rho.txt
CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat0.2_small_width_no_division.csv
PYTHON_SCRIPT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/single-run-analyze-counts.py

python $PYTHON_SCRIPT $TEXT > $CSV
```


```{r}
csv = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat0.2_small_width_no_division.csv")

# Plot the after dispersal counts
after_dispersal_ndd = plot_count_vs_exp(csv, "dd","after_dispersal",FALSE)
after_dispersal_ndwt = plot_count_vs_exp(csv, "dwt","after_dispersal",FALSE)
after_dispersal_wtdwt = plot_count_vs_exp(csv, "wtwt","after_dispersal",FALSE)

print(after_dispersal_ndd)
print(after_dispersal_ndwt)
print(after_dispersal_wtdwt)

# Plot the after reproduction counts
after_rep_dd = plot_count_vs_exp(csv, "dd","after_reproduction",FALSE)
after_rep_dwt = plot_count_vs_exp(csv, "dwt","after_reproduction",FALSE)
after_rep_wtwt = plot_count_vs_exp(csv, "wtwt","after_reproduction",FALSE)

print(after_rep_dd)
print(after_rep_dwt)
print(after_rep_wtwt)

# Plot the after reproduction + viability counts
after_viab_dd = plot_count_vs_exp(csv, "dd","after_viability",FALSE)
after_viab_dwt = plot_count_vs_exp(csv, "dwt","after_viability",FALSE)
after_viab_wtwt = plot_count_vs_exp(csv, "wtwt","after_viability",FALSE)

print(after_viab_dd)
print(after_viab_dwt)
print(after_viab_wtwt)
```
## Same width but dividing observed counts by the cell_width this time (as before)

Width of 0.01
```{bash eval=F}
TEXT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/m1000_k_uhat_0.2_N_rho.txt
CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat0.2_small_width_with_division.csv
PYTHON_SCRIPT=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/single-run-analyze-counts.py

python $PYTHON_SCRIPT $TEXT > $CSV
```


```{r}
csv = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_k_uhat0.2_small_width_with_division.csv")

# Plot the after dispersal counts
after_dispersal_ndd = plot_count_vs_exp(csv, "dd","after_dispersal",FALSE)
after_dispersal_ndwt = plot_count_vs_exp(csv, "dwt","after_dispersal",FALSE)
after_dispersal_wtdwt = plot_count_vs_exp(csv, "wtwt","after_dispersal",FALSE)

print(after_dispersal_ndd)
print(after_dispersal_ndwt)
print(after_dispersal_wtdwt)

# Plot the after reproduction counts
after_rep_dd = plot_count_vs_exp(csv, "dd","after_reproduction",FALSE)
after_rep_dwt = plot_count_vs_exp(csv, "dwt","after_reproduction",FALSE)
after_rep_wtwt = plot_count_vs_exp(csv, "wtwt","after_reproduction",FALSE)

print(after_rep_dd)
print(after_rep_dwt)
print(after_rep_wtwt)

# Plot the after reproduction + viability counts
after_viab_dd = plot_count_vs_exp(csv, "dd","after_viability",FALSE)
after_viab_dwt = plot_count_vs_exp(csv, "dwt","after_viability",FALSE)
after_viab_wtwt = plot_count_vs_exp(csv, "wtwt","after_viability",FALSE)

print(after_viab_dd)
print(after_viab_dwt)
print(after_viab_wtwt)
```

Things that could be wrong:

+ The calculation of the wild-type density