---
title: "Methods to control local density"
author: "Isabel Kim"
date: "5/31/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exponentiate the competition factor

* Get rid of the "a few generations only" `reproduction()` code. 
* In every generation, turn down the local density competition factor penalty by exponentiating this with a value less than 1

### Exponent of 0.5

* Nwt = 30,000
* drop size = 10,000 (25% introduction frequency)
* exponent = 0.5

* Observations:
  + Allee effects occur at least 3x in the simulation

```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-exp0.5.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-exp0.5.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
library(tidyverse)

output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/slim-output-exp0.5.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("introduction frequency of 25% \ncompetition factor exponent = 0.5")

print(plot_num_drive_alleles)
#ggsave(plot = plot_num_drive_alleles, filename = "/Users/isabelkim/Desktop/num_drive_alleles_exponent0.5.png")

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + ggtitle("introduction frequency of 25% \ncompetition factor exponent = 0.5")
print(plot_N_over_time)
#ggsave(plot = plot_N_over_time, filename = "/Users/isabelkim/Desktop/popsize_exponent0.5.png")
```

This *does* seem to still punish the drive in the first generation a lot. Plus, the population size doesn't stay at an equilibrium; it continues to increase.


### Exponent of 1/3

* Nwt = 30,000
* drop size = 10,000 (25% introduction frequency)
* exponent = 1/3

* Observations: 
  + Lots of clustering of the drive --> many individual can't find a mate.
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-exp-one-third.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-exp-one-third.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/slim-output-exp-one-third.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("introduction frequency of 25% \ncompetition factor exponent = 1/3")

print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + ggtitle("introduction frequency of 25% \ncompetition factor exponent = 1/3")
print(plot_N_over_time)
```

Same problem as before, and the population reaches an even higher level.

### Baseline: exponent of 1 -- how bad is the drive punishment problem?

* Nwt = 30,000
* drop size = 10,000 (25% introduction frequency)
* exponent = 1
* Observations
  + No cases where an individual can't find a mate
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-exp1.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-exp1.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/slim-output-exp1.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("introduction frequency of 25% \ncompetition factor exponent = 1")

print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + ggtitle("introduction frequency of 25% \ncompetition factor exponent = 1")
print(plot_N_over_time)
```
*BIG* drop in the number of drive alleles. Still no real "equilibrium" N.

## Set up a different interaction for local density control and make the radius bigger (originally was 0.001)

### distance = 0.01

* Nwt = 30,000
* drop size = 10,000 (25% introduction frequency)
* distance = 0.01
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-d0.01.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-d0.01.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/slim-output-d0.01.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("introduction frequency of 25% \ninteraction distance = 0.01")

print(plot_num_drive_alleles)
#ggsave(plot = plot_num_drive_alleles, filename = "/Users/isabelkim/Desktop/num_drive_alleles_interaction_distance_0.01.png")


plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + ggtitle("introduction frequency of 25% \ninteraction distance = 0.01")
print(plot_N_over_time)
ggsave(plot = plot_N_over_time, filename = "/Users/isabelkim/Desktop/popsize_interaction_distance_0.01.png")

```
Still a big drop in the number of drive alleles.

### distance = 0.05

* Nwt = 30,000
* drop size = 10,000 (25% introduction frequency)
* distance = 0.05
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-d0.05.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-d0.05.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/slim-output-d0.05.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("introduction frequency of 25% \ninteraction distance = 0.05")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + ggtitle("introduction frequency of 25% \ninteraction distance = 0.05")
print(plot_N_over_time)
```
Big drop still.

## Investigate the number of individuals surrounding a few of the d/d individuals released

Sampling 10 female d/d at generation 10 after release and dispersal (before reproduction in generation 11) for radius of 0.001
```{r}
number_around_female = c(557,832,453,614,613,392,222,334,97,371)
mean(number_around_female)

ratios = number_around_female/80 # ni/nexp
ratios

competition_factors = 2/(ratios + 1)
competition_factors

num_offspring_expected = 2*competition_factors
num_offspring_expected
```

for radius of 0.01:
```{r}
number_around_female = c(7026, 3888,7214,7197,6548,761,7147,7335,6780,6707)
mean(number_around_female)

ratios = number_around_female/800 # ni/nexp
ratios

competition_factors = 2/(ratios + 1)
competition_factors

num_offspring_expected = 2*competition_factors
num_offspring_expected

beta_comp = function(beta){
  denom = ((beta-1)*7.5)+1
  num = beta
  return(num/denom)
}

# find one around 1
betas = 2:11
comp_factors = rep(-1,10)
for (i in 1:10){
  comp_factors[i] = beta_comp(betas[i])
}

plot(betas,comp_factors)
```

As beta increases, clustered individuals are punished even more.

## Drop of 100 (0.33% introduction frequency)

### Keeping the local density radius = the mating radius and the exponent on the competition factor = 1

Using the `EXPECTED_ADULT_COMPETITION` term:

```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/using_term.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m100_using_expected_adult_competition.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
library(tidyverse)
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m100_using_expected_adult_competition.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 100 into 30,000")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 100 into 30,000")
print(plot_N_over_time)
```
The drive is lost and the population size fluctuates but is much below the capacity of 30,000.

Letting `EXPECTED_ADULT_COMPETITION` = the current population size
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/using_term.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m100_using_current_population_size.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

* Lots of Allee effects --> population crashes
```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m100_using_current_population_size.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 100 into 30,000")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 100 into 30,000")
print(plot_N_over_time)
```
Almost linear decrease in population size

### Increasing the local density radius to 0.01

With the standard `EXPECTED_ADULT_COMPETITION` term
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/using_term.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m100_standard_exp_and_increased_radius.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m100_standard_exp_and_increased_radius.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 100 into 30,000")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 100 into 30,000")
print(plot_N_over_time)
```
Population size stays more stable / doesn't crash.

