---
title: "Single run of SLiM -- number of drive alleles"
author: "Isabel Kim"
date: "5/30/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters

* sigma = 0.01 (D = 0.00005)
* k = 0.2
* uhat = 20%
  + d/d viability probability = 100%
  + d/wt viability probability = 74.2%
  + wt/wt viability probability = 80.6%
* mating radius = interaction distance = 0.001
* growth at zero density = 2
* generations where local density control is turned off in `reproduction()` = 5
  + from gen11-gen15
* wild-type population size = 30,000

## Python script planning

* Standard output line: `GEN:: 10 N:: 20333 NUM_DD:: 3000 NUM_DWT:: 0 NUM_WTWT:: 20333 NUM_D_ALLELES:: 6000 RATE_D:: 0.147543`
  + Python should grab lines that start with `GEN::` and in a csv output:
    1. Generation
    2. Population size
    3. Number of d/d
    4. Number of d/wt
    5. Number of wt/wt
    6. Number of drive alleles
    7. Rate of drive
* Python script `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/single-run-number-drive-alleles.py`
  + Pass in the path to the SLiM console text file. Pipe the output to a csv.

## Function to calculate the drop size given a desired introduction frequency

```{r}
drop_size_given_u0 = function(intro_freq,num_wts=30000){
  numerator = intro_freq*num_wts
  denominator = 1-intro_freq
  sol = numerator/denominator
  size = round(sol)
  return(size)
}
```


## Single run: introduction frequency of 25%

```{r}
drop_size_given_u0(0.25)
```

### Generations of no local density control = 5

* Text output file: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25.txt`

```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
library(tidyverse)

output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + geom_vline(xintercept=6) + ggtitle("introduction frequency of 25% \nlocal density control begins again at gen6")

#ggsave(plot = plot_num_drive_alleles, filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/figures/off_gens_11_to_15.png")

print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + geom_vline(xintercept=6) + ggtitle("introduction frequency of 25% \nlocal density control begins again at gen6")
print(plot_N_over_time)
```

Problem -- the number of drive alleles changes a lot once the local density control switch is turned back on. Population size declines a lot then increases at generation 5.

Turn this off for only 1 generation? Or use global density control during the time where local density control is off?

### Global density control; local is still off for 5 generations

* SLiM console text file: `/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-global-control.txt`

```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-global-control.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-global-control.csv

python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-global-control.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + geom_vline(xintercept=6) + ggtitle("introduction frequency of 25% \nlocal density control begins again at gen6 \nbut there's global density control during this time")

print(plot_num_drive_alleles)
#ggsave(plot = plot_num_drive_alleles, filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/figures/off_gens_11_to_15_global_density_control.png")

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + geom_vline(xintercept=6) + ggtitle("introduction frequency of 25% \nlocal density control begins again at gen6 \nbut there's global density control during this time")
print(plot_N_over_time)
```

Still big dips

### Try just 1 generation without local density control (generation 11)
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-1gen-only.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-1gen-only.csv

python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/slim-output-u0-25-1gen-only.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + geom_vline(xintercept=2) + ggtitle("introduction frequency of 25% \nlocal density control begins again at gen2")

print(plot_num_drive_alleles)
#ggsave(plot = plot_num_drive_alleles, filename = "/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/figures/off_in_gen11.png")

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + geom_vline(xintercept=2) + ggtitle("introduction frequency of 25% \nlocal density control begins again at gen2")
print(plot_N_over_time)
```

