---
title: "2-step density control"
author: "Isabel Kim"
date: "6/6/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Function

```{r}
additional_number_of_offspring = function(local_number, expected_number, max_addition, factor){
  sol = max_addition*exp((-factor*local_number)/expected_number)
  return(sol)
}
```

## Looping through different decay factors
```{r}
library(tidyverse)
decay_factor = 5
expected_number=60
max_addition=10

local_numbers = seq(0,100)
addition = rep(-1,length(local_numbers))

for (i in 1:length(local_numbers)){
  local = local_numbers[i]
  addition[i] = additional_number_of_offspring(local,expected_number,max_addition,decay_factor)
}
t = tibble(local_density = local_numbers, additional_num_offspring = addition)
g = ggplot(t,aes(x = local_density, y = additional_num_offspring)) + geom_line(color = "green")+theme_minimal() + geom_vline(xintercept = 0) + geom_hline(yintercept = 0) + ggtitle(paste0(max_addition,"e^{-",decay_factor,"ni/nexp}"))
print(g)

ggsave(filename = "/Users/isabelkim/Desktop/additional_number_offspring_when_exp60.png",plot = g)
```
Let's go with 5.


## Plotting the number of drive alleles and population size

### Initial -- additional = 10*exp(-5competition_factor) and global fitnessScaling with capacity = WT_SIZE + DROP_SIZE

```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/initial_two_step.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/initial_two_step.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/initial_two_step.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 100 into 30,000")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 100 into 30,000")
print(plot_N_over_time)
```
* Population size is staying pretty constant
* The number of drive alleles declines but with a pretty normal shape

### Increase drop size to 1000
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/two_step_m1000.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/two_step_m1000.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/two_step_m1000.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 1000 into 30,000")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 1000 into 30,000")
print(plot_N_over_time)
```
Really weird shape. Population size (and number of drive alleles) increases ~linearly towards the end (because of viability selection)? Try decreasing the capacity to 30,000 again and running the simulation for longer. Once the drive allele has fixed, the population size should stabilize.

### Decrease global capacity to 30,000 and run simulation longer (drop size still 1000)
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/m1000_two_step.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_two_step_capacity_30k.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/m1000_two_step_capacity_30k.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 1000 into 30,000")
print(plot_num_drive_alleles)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 1000 into 30,000")
print(plot_N_over_time)
```
Is this increase okay?

## Checks: set k=0 s.t. the drive doesn't have any fitness advantage. Drop size of 1000 (3% introduction frequency)

The population size and number of drive alleles should stay ~ constant
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/checks_m1000.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/checks_m1000.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/checks_m1000.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 1000 into 30,000")
print(plot_num_drive_alleles)

plot_rate_drive = ggplot(output, aes(x = gen, y = rate_d_alleles)) + theme_minimal() + ylim(0,0.035)+
  geom_line(color = "orange") + xlab("gen") + ylab("rate of drive alleles") + ggtitle("Drop size of 1000 into 30,000")
print(plot_rate_drive)

plot_N_over_time = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 1000 into 30,000")
print(plot_N_over_time)
```
Why does the number of drive alleles dip and then increase ~gen50? Re-run and see if this happens again... 

Population size stays pretty constant.


## Checks: set k=0 round 2

```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/checks_m1000.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/second_checks_m1000.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/second_checks_m1000.csv")

gen = c(-9:-1, output$gen)
num_d = c(rep(0,9),output$num_d_alleles)
rate_d = c(rep(0,9), output$rate_d_alleles)
popsize_vec = c(30000, 29954, 29922, 30199, 29955, 30138, 30043, 30025, 29694,output$popsize)
full_info = tibble(gen = gen, num_d_alleles = num_d, rate_d_alleles = rate_d, popsize = popsize_vec)

plot_num_drive_alleles = ggplot(full_info, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 1000 into 30,000") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0)
print(plot_num_drive_alleles)

plot_rate_drive = ggplot(full_info, aes(x = gen, y = rate_d_alleles)) + theme_minimal() + ylim(0,0.035)+
  geom_line(color = "orange") + xlab("gen") + ylab("rate of drive alleles") + ggtitle("Drop size of 1000 into 30,000") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0)

print(plot_rate_drive)

plot_N_over_time = ggplot(full_info, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 1000 into 30,000") + 
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0) + ylim(min(full_info$popsize),max(full_info$popsize))

print(plot_N_over_time)

#ggsave(filename = "/Users/isabelkim/Desktop/rate_of_drive.png", plot = plot_rate_drive)
#ggsave(filename = "/Users/isabelkim/Desktop/num_drive_alleles.png", plot = plot_num_drive_alleles)
#ggsave(filename = "/Users/isabelkim/Desktop/population_size.png", plot = plot_N_over_time)

# MESSED UP N HERE
zoom_in_N = plot_N_over_time + xlim(-9,50)
#ggsave(filename = "/Users/isabelkim/Desktop/population_size_till_gen50.png", plot = zoom_in_N)
```

## Checks: set k=0 round 3 (but add the pre-drop popsize info this time)
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/checks_m1000.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/third_checks_m1000.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/third_checks_m1000.csv")

gen = c(-9:-1, output$gen)
num_d = c(rep(0,9),output$num_d_alleles)
rate_d = c(rep(0,9), output$rate_d_alleles)
popsize_vec = c(30000, 30155, 30045, 30023, 30139, 30092, 30079, 29961, 29986,output$popsize)
full_info = tibble(gen = gen, num_d_alleles = num_d, rate_d_alleles = rate_d, popsize = popsize_vec)

plot_num_drive_alleles = ggplot(full_info, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 1000 into 30,000") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0)
print(plot_num_drive_alleles)

plot_rate_drive = ggplot(full_info, aes(x = gen, y = rate_d_alleles)) + theme_minimal() + ylim(0,0.035)+
  geom_line(color = "orange") + xlab("gen") + ylab("rate of drive alleles") + ggtitle("Drop size of 1000 into 30,000") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0)

print(plot_rate_drive)

plot_N_over_time = ggplot(full_info, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 1000 into 30,000") + 
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0) + ylim(min(full_info$popsize),max(full_info$popsize))

print(plot_N_over_time)

#ggsave(filename = "/Users/isabelkim/Desktop/rate_of_drive.png", plot = plot_rate_drive)
#ggsave(filename = "/Users/isabelkim/Desktop/num_drive_alleles.png", plot = plot_num_drive_alleles)
#ggsave(filename = "/Users/isabelkim/Desktop/population_size.png", plot = plot_N_over_time)

zoom_in_N = ggplot(full_info, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") +ggtitle("Drop size of 1000 into 30,000") + 
 geom_hline(yintercept = 0) + ylim(min(full_info$popsize),max(full_info$popsize))+ xlim(-9,50)
#ggsave(filename = "/Users/isabelkim/Desktop/population_size_till_gen50.png", plot = zoom_in_N)

```

## When there *are* fitness differences

* k = uhat = 0.2
* d/d fitness = 1.0
* d/wt fitness = 0.741935
* wt/wt fitness = 0.806452
```{bash eval=F}
SLIM_CONSOLE=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/text_out/output.txt
OUTPUT_CSV=/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/k_uhat0.2_m1000.csv

cd /Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files
python single-run-number-drive-alleles.py $SLIM_CONSOLE > $OUTPUT_CSV
```

```{r}
output = read_csv("/Users/isabelkim/Desktop/year2/underdominance/reaction-diffusion/new-slim-diffusion-files/csv_out/k_uhat0.2_m1000.csv")

plot_num_drive_alleles = ggplot(output, aes(x = gen, y = num_d_alleles)) + theme_minimal() +
  geom_line(color = "red") + xlab("gen") + ylab("number of drive alleles") + ggtitle("Drop size of 1000 into 30,000 \nuhat=k=0.2") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0)
print(plot_num_drive_alleles)

plot_rate_drive_alleles = ggplot(output, aes(x = gen, y = rate_d_alleles)) + theme_minimal() +
  geom_line(color = "orange") + xlab("gen") + ylab("drive allele frequency") + ggtitle("Drop size of 1000 into 30,000 \nuhat=k=0.2") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0) + ylim(0,1)
print(plot_rate_drive_alleles) 

plot_popsize = ggplot(output, aes(x = gen, y = popsize)) + theme_minimal() +
  geom_line(color = "purple") + xlab("gen") + ylab("population size") + ggtitle("Drop size of 1000 into 30,000 \nuhat=k=0.2") +
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0) + ylim(min(output$popsize), max(output$popsize))

print(plot_popsize) 
```
Population size increases more because the wild-types have lower viability selection before the drive is present.